\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-03-19 paper.qmd
Rescale total number of bin plots

>>>>

```{r}
#| echo: false
#| message: false
#| warning: false

num_bins_x <- 3
num_bins_y <- 4
hex_size <- 0.62

## Data set with all possible centroids in the hexagonal grid
all_centroids_df <- as.data.frame(do.call(cbind, hb_obj$centroids))
counts_df <- as.data.frame(do.call(cbind, hb_obj$std_cts))

hex_full_count_df_loop1 <- dplyr::left_join(hex_grid, counts_df, by = c("hex_poly_id" = "hb_id"))

p1 <-  ggplot(data = hex_full_count_df_loop1, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = hex_poly_id, fill = std_counts)) +
  geom_point(data = umap_s_curve_scaled, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  #coord_equal() +
  coord_cartesian(xlim =c(-0.2, 1.2), ylim = c(-0.1, 2.5)) +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) +
  annotate(geom = 'text', label = "a", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

```{r}
#| echo: false
#| message: false
#| warning: false

num_bins_x <- 6
num_bins_y <- 14
hex_size <- 0.13

## Data set with all possible centroids in the hexagonal grid
all_centroids_df <- as.data.frame(do.call(cbind, hb_obj$centroids))
counts_df <- as.data.frame(do.call(cbind, hb_obj$std_cts))

hex_full_count_df_loop2 <- dplyr::left_join(hex_grid, counts_df, by = c("hex_poly_id" = "hb_id"))

p2 <-  ggplot(data = hex_full_count_df_loop2, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = hex_poly_id, fill = std_counts)) +
  geom_point(data = umap_s_curve_scaled, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  #coord_equal() +
  coord_cartesian(xlim =c(-0.2, 1.2), ylim = c(-0.1, 2.5)) +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) +
  annotate(geom = 'text', label = "b", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

```{r}
#| echo: false
#| message: false
#| warning: false

num_bins_x <- 12
num_bins_y <- 28
hex_size <- 0.06

## Data set with all possible centroids in the hexagonal grid
all_centroids_df <- as.data.frame(do.call(cbind, hb_obj$centroids))
counts_df <- as.data.frame(do.call(cbind, hb_obj$std_cts))

hex_full_count_df_loop3 <- dplyr::left_join(hex_grid, counts_df, by = c("hex_poly_id" = "hb_id"))

p3 <-  ggplot(data = hex_full_count_df_loop3, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = hex_poly_id, fill = std_counts)) +
  geom_point(data = umap_s_curve_scaled, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  coord_equal() +
  #coord_cartesian(xlim =c(-1, 2.7), ylim = c(-2, 12.2)) +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) +
  annotate(geom = 'text', label = "c", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

```{r}
#| echo: false
#| label: fig-binsize
#| fig-pos: H
#| fig-cap: "Hexbin plots from different number of bins for the **UMAP** embeddings of **S-curve** training data: (a) b = 12 (3, 4), h = 0.62, (b) b = 84 (6, 14), h = 0.13, and (c) b = 336 (12, 28), h = 0.06. The hexbins are colored based on the density of points, with darker colors indicating higher point density and yellow color representing lower point density within each bin. What is the number of bins that would be effective in representing low-dimensional data?"

### 2024-03-19 paper.tex
Rescale total number of bin plots

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, boxrule=0pt, sharp corners, breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable, frame hidden]}{\end{tcolorbox}}\fi
